---
title: CV
name: Dr. Dana
surname: Calacci
position: "Assistant Professor, Penn State University College of IST"
address: "State College, PA"
phone: +1 908 229 8992
pronouns: she/her
www: "dcalacci.net"
email: "dana@dcalacci.net"
github: dcalacci
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "I build participatory tools and evaluation methods that shift access toward communities, enabling them to investigate algorithmic systems, generate evidence of harm, and build collective power."
header-includes:
  - \definecolor{headcolor}{HTML}{000000}
  - \usepackage{xcolor}
output:
  vitae::hyndman:
    latex_engine: pdflatex
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
library(dplyr)
# Store surname from YAML metadata for use in custom functions
# Parse YAML front matter to extract surname
surname <- NULL
if (requireNamespace("yaml", quietly = TRUE)) {
  tryCatch({
    # Read the current Rmd file and parse YAML front matter
    input_file <- knitr::current_input()
    if (!is.null(input_file) && file.exists(input_file)) {
      lines <- readLines(input_file)
      yaml_end <- grep("^---\\s*$", lines)[2]
      if (!is.na(yaml_end) && yaml_end > 1) {
        yaml_text <- paste(lines[1:yaml_end], collapse = "\n")
        meta <- yaml::yaml.load(yaml_text)
        if (!is.null(meta$surname)) {
          surname <- meta$surname
        }
      }
    }
  }, error = function(e) {
    # If parsing fails, surname will remain NULL
  })
}
# Store surname in knitr options for use in custom functions
knitr::opts_knit$set(cv_surname = surname)
source("custom_hyndman.R")
```


# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD, Media Arts and Sciences", "2019-2023", "Massachusetts Institute of Technology", "Cambridge, MA",
  "M.S., Media Arts and Sciences", "2016-2018", "Massachusetts Institute of Technology", "Cambridge, MA",
  "B.S., Computer Science", "2011-2015", "Northeastern University", "Boston, MA"
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```

# Appointments

```{r}
tribble(
  ~ Institution, ~ Year, ~ Department, ~ Title, 
  "Penn State University", "2024-", "College of Information Sciences and Technology", "Assistant Professor",
  "Penn State University", "2024-", "Institute for Computational and Data Sciences", "Co-Hire & Affiliate",
  "Princeton University", "2023-2024", "Center for Information Technology Policy", "Postdoctoral Fellow",
  "MIT Media Lab", "2023-", "Human Dynamics Group", "Research Affiliate"
) %>% 
  detailed_entries(Institution, Year, Department, Title)
```

# Refereed Articles
```{r, hidden=TRUE}
contributions <- read.csv('contributions.csv') %>%
  tibble()
```

```{r}
contributions %>%
  filter(Section == 'Refereed Article') %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL)
```

## Under Review

```{r}
contributions %>%
  filter(Section == 'Under Review') %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL)
```

## Selected Other Publications

```{r}
contributions %>%
  filter(Section == 'Public Writing') %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL, show_venue_short = FALSE)
```


# Conference & Workshop Participation

## Keynotes

```{r}
contributions %>%
  filter(Section == 'Keynote') %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL)
```

## Organizer
```{r}
contributions %>%
  filter(Section == 'Organized Events') %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL, show_venue_short = FALSE)
```

## Talks
```{r}
contributions %>%
  filter(Section %in% c('Conference Talk')) %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL, show_venue_short = TRUE)
```

## Posters
```{r}
contributions %>%
  filter(Section %in% c('Poster')) %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL, show_venue_short = TRUE)
```


# Grants 

## Current

```{r}
tribble(
  ~Year, ~Title, ~Role, ~Funder,
  "2025", "Mapping Language Model Failures through Community Experience: A Study of Multilingual Researchers", "Penn State Institute for Computational and Data Sciences Rising Researcher", "PI, (~$30,000 2y)",
  "2025", "From Evaluation to Alignment: Toward Community-Aligned AI", "Penn State Institute for Computational and Data Sciences Faculty Upskilling Fellowship ($27,000, 1y)",  "PI, ($27,000, 1y)",
  "2024", "Empowering Delivery Gig Workers with Data and Insights to Improve Health", "Robert Wood Johnson Foundation Pioneering Ideas (total $250,000, 3y)", "Key Personnel",
) %>%
  publication_entries(Title, Year, Role, Funder, "", "", show_venue_short=FALSE)
```

## Submitted & Under Review

```{r}
tribble(
  ~Year, ~Title, ~Role, ~Funder,
  "2025", "From Evaluation to Alignment: Toward Community-Aligned AI", "Sloan Research Fellowship", "PI, $70,000",
  "2025", "Gig Work and Health Inequalities: Evidence From the Food Delivery Labor Market", "National Institutes of Health (total $3,391,570 total, 5y)", "Co-PI (Subaward: $253,359)"
) %>%
  publication_entries(Title, Year, Role, Funder, "", "", show_venue_short=FALSE)
```

## Completed

```{r}
tribble(
  ~Year, ~Title, ~Role, ~Funder,
  "2022", "The Worker's Observatory: Crowdsourced tools for Collective Audits of Algorithmic Systems in the Gig Economy", "Mozilla Technology Fund ($50,000)",  "Co-PI",
  "2018", "SBIR Phase I: Positive Effects of Feedback and Intervention for Engagement in Online Learning", "National Science Foundation #1843391 ($223,090)", "Co-PI",
  "2020", "SBIR Phase II: Using Intervention and Feedback to Improve Group Function In Online Contexts", "National Science Foundation #2026003 ($991,417)", "Key Personnel & Co-author",
) %>%
  publication_entries(Title, Year, Role, Funder, "", "", show_venue_short=FALSE)
```


# Invited Talks

```{r}
contributions %>%
  filter(Section == 'Invited Talk') %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL, show_venue_short = FALSE)
```

# Campus & Departmental Talks
```{r}
contributions %>%
  filter(Section == 'Internal Talk') %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL, show_venue_short = FALSE)
```

# Teaching Experience

```{r}
tribble(
  ~Year, ~Title, ~Where, ~Description,
  "2025", "Community AI Development and Evaluation (IST 597)", "Penn State IST", "Graduate seminar on developing and evaluating AI systems with a community focus",
  "2024", "DS 435 Data Ethics", "Penn State IST", "Required class for Data Science majors; redesigned from scratch with co-learning and peer evaluation"
) %>%
  detailed_entries(Title, Year, Where, "", c(Description))
```

# Student Advising and Mentorship



## Direct Advisor

```{r}
tribble(
  ~Year, ~Title, ~Authors, ~Venue,
  "2025-26", "Tianqi Kou", "Toward a Feminist Conception of Replicability for Machine Learning Research", "Penn State IST",
  "2028-29", "Brea Austin", "", "Penn State IST",
  "2028-29", "Matt Viana", "", "Penn State IST"
) %>%
  detailed_entries(Title, Year, Venue, Authors)
```

## Committee Membership
````{r}
students <- read.csv("students.csv")

students %>%
  filter(Type == "Committee") %>%
  arrange(desc(Year), Institution) %>%
  detailed_entries(Name, Year, Institution, Notes)
````

## Mentorship
````{r}
students %>%
  filter(Type == "Mentorship") %>%
  arrange(desc(Year)) %>%
  detailed_entries(Name, Year, Institution, Notes)
````

## Undergraduate Mentorship & Advising
```{r}
students %>%
  filter(Type == "Undergraduate") %>%
  arrange(desc(Year)) %>%
  detailed_entries(Name, Year, Institution, Notes)
```


# Professional Service

```{r}
tribble(
  ~Year, ~Title, ~Authors, ~Venue,
  "", "CHI, CSCW, (e)CSCW, FAccT, Big Data & Society, SBP-BRiMS, PLOS-One, Nature", "Reviewer", "",
  "", "FAccT", "AC", "",
) %>%
  detailed_entries(Title, Year, Venue, Authors)
```

# University Service

```{r}
tribble(
  ~Year, ~Title, ~Authors, ~Venue,
  "2025-26", "Artificial Intelligence Hiring Committee", "", "Penn State IST",
  "2024-25", "Privacy & Security Hiring Committee", "", "Penn State IST",
  "2025", "Panelist, Women's History Month in STEM Event", "", "Penn State",
  "2025", "Judge, Penn State IDEAMakers Startup Challenge", "", "Penn State",
  "2025", "Panelist, LGBTQ+ In Tech", "", "Penn State"
) %>%
  detailed_entries(Title, Year, Venue, Authors)
```

# Selected Media Coverage

```{r}
contributions %>%
  filter(Section %in% c('Media Coverage')) %>%
  arrange(desc(Year)) %>%
  media_entries(Title, Year, Venue, URL)
```

# Other Professional Experience

```{r}
tribble(
  ~Year, ~Title, ~Authors, ~Venue,
  "2020-", "WeClock", "Researcher In Residence", "Design, develop, and deploy worker-centric labor technology; advise on grant applications; run workshops with trade union leaders",
  "2020", "NASA/JPL", "Media Artist", "Conceptualized and executed artistic projects investigating the epistemology of scientific research and visualization",
  "2018-2019", "Riff Analytics", "Cofounder and Chief Research Scientist", "Led AI and data science pipeline, product architecture, and research designs; co-wrote successful NSF SBIR grant"
) %>%
  detailed_entries(Title, Year, Venue, Authors)
```
