---
title: CV
name: Dr. Jane
surname: Smith
position: "Assistant Professor, State University"
address: "City, State"
phone: +1 555 123 4567
pronouns: she/her
www: "example.net"
email: "jane.smith@example.edu"
github: janesmith
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "My research focuses on ethical AI, algorithmic fairness, and the societal impacts of machine learning systems."
header-includes:
  - \definecolor{headcolor}{HTML}{000000}
  - \usepackage{xcolor}
output:
  vitae::hyndman:
    latex_engine: pdflatex
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
library(dplyr)
# Store surname from YAML metadata for use in custom functions
# Parse YAML front matter to extract surname
surname <- NULL
if (requireNamespace("yaml", quietly = TRUE)) {
  tryCatch({
    # Read the current Rmd file and parse YAML front matter
    input_file <- knitr::current_input()
    if (!is.null(input_file) && file.exists(input_file)) {
      lines <- readLines(input_file)
      yaml_end <- grep("^---\\s*$", lines)[2]
      if (!is.na(yaml_end) && yaml_end > 1) {
        yaml_text <- paste(lines[1:yaml_end], collapse = "\n")
        meta <- yaml::yaml.load(yaml_text)
        if (!is.null(meta$surname)) {
          surname <- meta$surname
        }
      }
    }
  }, error = function(e) {
    # If parsing fails, surname will remain NULL
  })
}
# Store surname in knitr options for use in custom functions
knitr::opts_knit$set(cv_surname = surname)
source("custom_hyndman.R")
```


# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Ph.D., Computer Science", "2018-2022", "Research University", "City, State",
  "M.S., Computer Science", "2016-2018", "State University", "City, State",
  "B.S., Mathematics", "2012-2016", "Liberal Arts College", "City, State"
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```

# Appointments

```{r}
tribble(
  ~ Institution, ~ Year, ~ Department, ~ Title, 
  "State University", "2023-", "Computer Science Department", "Assistant Professor",
  "Research University", "2022-2023", "Center for AI Research", "Postdoctoral Fellow"
) %>% 
  detailed_entries(Institution, Year, Department, Title)
```

# Refereed Articles
```{r, hidden=TRUE}
contributions <- read.csv('contributions.csv') %>%
  tibble()
```

```{r}
contributions %>%
  filter(Section == 'Refereed Article') %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL)
```

## Under Review

```{r}
contributions %>%
  filter(Section == 'Under Review') %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL)
```

## Selected Other Publications

```{r}
contributions %>%
  filter(Section == 'Public Writing') %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL, show_venue_short = FALSE)
```


# Conference & Workshop Participation

## Keynotes

```{r}
contributions %>%
  filter(Section == 'Keynote') %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL)
```

## Organizer
```{r}
contributions %>%
  filter(Section == 'Organized Events') %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL, show_venue_short = FALSE)
```

## Talks
```{r}
contributions %>%
  filter(Section %in% c('Conference Talk')) %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL, show_venue_short = TRUE)
```

## Posters
```{r}
contributions %>%
  filter(Section %in% c('Poster')) %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL, show_venue_short = TRUE)
```


# Grants 

## Current

```{r}
tribble(
  ~Year, ~Title, ~Role, ~Funder,
  "2025", "AI Ethics Research Grant", "State University Research Fund", "PI, ($25,000, 2y)",
  "2024", "Algorithmic Fairness Study", "Example Foundation", "Co-PI, ($50,000, 1y)"
) %>%
  publication_entries(Title, Year, Role, Funder, "", "", show_venue_short=FALSE)
```

## Submitted & Under Review

```{r}
tribble(
  ~Year, ~Title, ~Role, ~Funder,
  "2025", "Future AI Research Project", "Example Fellowship", "PI, $50,000"
) %>%
  publication_entries(Title, Year, Role, Funder, "", "", show_venue_short=FALSE)
```

## Completed

```{r}
tribble(
  ~Year, ~Title, ~Role, ~Funder,
  "2022", "AI Ethics Tool Development", "Example Foundation ($40,000)", "Co-PI",
  "2020", "Machine Learning Research Grant", "National Science Foundation ($200,000)", "Key Personnel"
) %>%
  publication_entries(Title, Year, Role, Funder, "", "", show_venue_short=FALSE)
```


# Invited Talks

```{r}
contributions %>%
  filter(Section == 'Invited Talk') %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL, show_venue_short = FALSE)
```

# Campus & Departmental Talks
```{r}
contributions %>%
  filter(Section == 'Internal Talk') %>%
  arrange(desc(Year)) %>%
  publication_entries(Title, Year, Authors, Venue, VenueShort, URL, show_venue_short = FALSE)
```

# Teaching Experience

```{r}
tribble(
  ~Year, ~Title, ~Where, ~Description,
  "2024", "AI Ethics", "State University", "Graduate seminar on ethical AI development",
  "2023", "Introduction to Machine Learning", "State University", "Undergraduate course on ML fundamentals"
) %>%
  detailed_entries(Title, Year, Where, "", c(Description))
```

# Student Advising and Mentorship



## Direct Advisor

```{r}
tribble(
  ~Year, ~Title, ~Authors, ~Venue,
  "2024-", "Alex Chen", "Example Dissertation Topic", "State University",
  "2025-", "Jordan Kim", "", "State University"
) %>%
  detailed_entries(Title, Year, Venue, Authors)
```

## Committee Membership
````{r}
students <- read.csv("students.csv")

students %>%
  filter(Type == "Committee") %>%
  arrange(desc(Year), Institution) %>%
  detailed_entries(Name, Year, Institution, Notes)
````

## Mentorship
````{r}
students %>%
  filter(Type == "Mentorship") %>%
  arrange(desc(Year)) %>%
  detailed_entries(Name, Year, Institution, Notes)
````

## Undergraduate Mentorship & Advising
```{r}
students %>%
  filter(Type == "Undergraduate") %>%
  arrange(desc(Year)) %>%
  detailed_entries(Name, Year, Institution, Notes)
```


# Professional Service

```{r}
tribble(
  ~Year, ~Title, ~Authors, ~Venue,
  "", "CHI, CSCW, (e)CSCW, FAccT, Big Data & Society, SBP-BRiMS, PLOS-One, Nature", "Reviewer", "",
  "", "FAccT", "AC", "",
) %>%
  detailed_entries(Title, Year, Venue, Authors)
```

# University Service

```{r}
tribble(
  ~Year, ~Title, ~Authors, ~Venue,
  "2024-25", "Faculty Search Committee", "", "State University",
  "2024", "Department Service Committee", "", "State University"
) %>%
  detailed_entries(Title, Year, Venue, Authors)
```

# Selected Media Coverage

```{r}
contributions %>%
  filter(Section %in% c('Media Coverage')) %>%
  arrange(desc(Year)) %>%
  media_entries(Title, Year, Venue, URL)
```

# Other Professional Experience

```{r}
tribble(
  ~Year, ~Title, ~Authors, ~Venue,
  "2021-2022", "Tech Company", "Research Consultant", "Advised on AI ethics and fairness in product development",
  "2019-2020", "Research Lab", "Research Assistant", "Conducted research on machine learning applications"
) %>%
  detailed_entries(Title, Year, Venue, Authors)
```
